---
title: "Detecting forced labor in fisheries - Econ model Proof of Concept"
author: Sustainable Fisheries Group, UCSB
output: html_notebook
---

# Setup
```{r}
library(tidyverse)
library(bigrquery)
project <-  "ucsb-gfw"
```

# Create relevant vessel table

Let's first look at US trawlers. We do not expect to see any forced labor in this fleet.

```{r}
# First, get all relevant vessel info

flag_poc <- "USA"
gear_poc <- "trawlers"

flag_poc <- "THA"

sql<-glue::glue("
#standardSQL
SELECT
mmsi,
year,
best_flag,
best_label,
best_tonnage,
best_length,
best_engine_power
FROM `world-fishing-827.gfw_research.vessel_info_20180518`
WHERE
best_flag = '{flag_poc}'
# AND best_label = '{gear_poc}'")

# Run new query. Delete old table, upload new one
bq_table(project = project,table = "poc_vessel_info",dataset = "human_rights") %>% 
  bq_table_delete()
bq_project_query(project,sql, destination_table = bq_table(project = project,table = "poc_vessel_info",dataset = "human_rights"),use_legacy_sql = FALSE, allowLargeResults = TRUE)
```


# Create table of all fishing voyages between 2012-2017 for that fleet

```{r}
sql <-"
#standardSQL
WITH
master AS(SELECT
anchorages.mmsi mmsi,
anchorages.from_anchorage_id from_anchorage_id,
CONCAT(b.anchor_group,
'-',
b.label) from_anchorage_name,
b.label from_port_name,
anchorages.departure_timestamp departure_timestamp,
anchorages.to_anchorage_id to_anchorage_id,
CONCAT(c.anchor_group,
'-',
c.label) to_anchorage_name,
c.label to_port_name,
anchorages.arrival_timestamp arrival_timestamp,
anchorages.flag flag,
anchorages.gear gear,
anchorages.tonnage tonnage,
anchorages.length length,
anchorages.engine_power engine_power
FROM (
SELECT
anchor1.mmsi mmsi,
anchor2.best_flag flag,
anchor2.best_label gear,
anchor2.best_tonnage tonnage,
anchor2.best_length length,
anchor2.best_engine_power engine_power,
anchor2.anchorage_id from_anchorage_id,
anchor2.event_end departure_timestamp,
anchor1.anchorage_id to_anchorage_id,
anchor1.event_start arrival_timestamp
FROM (
SELECT
vessel_1_id mmsi,
event_start,
event_end,
anchorage_id,
ROW_NUMBER() OVER (PARTITION BY vessel_1_id ORDER BY event_start) rn
FROM
`world-fishing-827.gfw_research.voyage_events_all_vessels_20180307`
WHERE
event_type = 'anchorage'
AND vessel_1_id IN (
SELECT
mmsi
FROM
`human_rights.poc_vessel_info`)) anchor1
JOIN (
SELECT
*,
rn+1 rn_plus
FROM ( (
SELECT
vessel_1_id mmsi,
EXTRACT(YEAR FROM event_start) AS year,
event_start,
event_end,
anchorage_id,
ROW_NUMBER() OVER (PARTITION BY vessel_1_id ORDER BY event_start) rn
FROM
`world-fishing-827.gfw_research.voyage_events_all_vessels_20180307`
WHERE
event_type = 'anchorage') voy_info
LEFT JOIN (
SELECT
mmsi mmsi_info,
year year_info,
best_flag,
best_label,
best_tonnage,
best_length,
best_engine_power
FROM
`human_rights.poc_vessel_info`) ves_info
ON
voy_info.mmsi = ves_info.mmsi_info
AND voy_info.year = ves_info.year_info)) anchor2
ON
anchor1.mmsi = anchor2.mmsi
AND anchor1.rn = anchor2.rn_plus) anchorages
LEFT JOIN (
SELECT
s2id,
label,
anchor_group
FROM
`world-fishing-827.gfw_research.named_anchorages_20171120`) b
ON
anchorages.from_anchorage_id = b.s2id
LEFT JOIN (
SELECT
s2id,
label,
anchor_group
FROM
`world-fishing-827.gfw_research.named_anchorages_20171120`) c
ON
anchorages.to_anchorage_id = c.s2id
)

SELECT
*
FROM
master
WHERE
NOT gear IS NULL
"

# Using better table

sql <-"
#standardSQL
  WITH master AS(
  SELECT
    anchorages.mmsi mmsi,
    anchorages.flag flag,
    anchorages.gear gear,
    anchorages.engine_power engine_power,
    anchorages.departure_timestamp departure_timestamp,
    anchorages.arrival_timestamp arrival_timestamp,
    anchorages.departure_port departure_port,
    anchorages.arrival_port arrival_port
  FROM (
    SELECT
      anchor1.mmsi mmsi,
      anchor2.best_flag flag,
      anchor2.best_label gear,
      anchor2.best_engine_power engine_power,
      anchor2.port_exit_timestamp departure_timestamp,
      anchor1.port_entry_timestamp arrival_timestamp,
      anchor2.port departure_port,
      anchor1.port arrival_port
    FROM (
      SELECT
        vessel_id mmsi,
        port_entry_timestamp,
        port_exit_timestamp,
        port_label port,
        ROW_NUMBER() OVER (PARTITION BY vessel_id ORDER BY port_entry_timestamp) rn
      FROM
        `world-fishing-827.gfw_research.port_entry_exit_only_20180121`
      WHERE
        vessel_id IN (
        SELECT
          mmsi
        FROM
          `human_rights.poc_vessel_info`)) anchor1
    JOIN (
      SELECT
        *,
        rn+1 rn_plus
      FROM ( (
          SELECT
            vessel_id mmsi,
            EXTRACT(YEAR
            FROM
              port_exit_timestamp) AS year,
            port_entry_timestamp,
            port_exit_timestamp,
            port_label port,
            ROW_NUMBER() OVER (PARTITION BY vessel_id ORDER BY port_entry_timestamp) rn
          FROM
            `world-fishing-827.gfw_research.port_entry_exit_only_20180121`) voy_info
        LEFT JOIN (
          SELECT
            mmsi mmsi_info,
            year year_info,
            best_flag,
            best_label,
            best_engine_power
          FROM
            `human_rights.poc_vessel_info`) ves_info
        ON
          voy_info.mmsi = ves_info.mmsi_info
          AND voy_info.year = ves_info.year_info)) anchor2
    ON
      anchor1.mmsi = anchor2.mmsi
      AND anchor1.rn = anchor2.rn_plus) anchorages)
SELECT
  *
FROM
  master
"
  

bq_table(project = project,table = "poc_voyages_with_anchorages",dataset = "human_rights") %>% 
  bq_table_delete()

bq_project_query(project,sql, destination_table = bq_table(project = project,table = "poc_voyages_with_anchorages",dataset = "human_rights"),
                 use_legacy_sql = FALSE, allowLargeResults = TRUE)
```

# Extract all events during those voyages
Events includes possible encounters (transshipment, bunkering, or fishing-to-fishing) and AIS coverage gaps

```{r}
sql<-"
#standardSQL
  WITH transshipment_ids AS(
  SELECT
    transshipment_vessel_id trans_mmsi
  FROM
    `world-fishing-827.gfw_research.encounters_fishing_transshipment_20180327`),
  bunker_ids AS(
  SELECT
    mmsi bunker_mmsi
  FROM
    `world-fishing-827.gfw_research.bunker_vessels_11072017` ),
  fishing_ids AS(
  SELECT
    mmsi fishing_mmsi
  FROM
    `world-fishing-827.gfw_research.vessel_info_20180518`
  WHERE
    on_fishing_list_nn ),
  event_table AS(
  SELECT
    vessel_1_id,
    vessel_2_id,
    event_start,
    event_end,
    event_type
  FROM
    `world-fishing-827.gfw_research.voyage_events_all_vessels_20180307`
  WHERE
    event_type = 'rendezvous'
    OR event_type = 'coverage gap'),
  voyages AS(
  SELECT
    mmsi,
    departure_timestamp,
    departure_port,
    arrival_timestamp,
    arrival_port
  FROM
    `human_rights.poc_voyages_with_anchorages`),
  joined_table AS(
  SELECT
    *
  FROM
    event_table
  JOIN
    voyages
  ON
    (event_table.vessel_1_id = voyages.mmsi
      OR event_table.vessel_2_id = voyages.mmsi)
    AND event_table.event_start >voyages.departure_timestamp
    AND event_table.event_end < voyages.arrival_timestamp),
final_event_table AS(SELECT
  mmsi,
  departure_timestamp,
  departure_port,
  arrival_timestamp,
  arrival_port,
  (CASE
      WHEN event_type = 'rendezvous' AND (vessel_1_id IN (  SELECT  trans_mmsi  FROM  transshipment_ids) OR vessel_2_id IN (  SELECT  trans_mmsi  FROM  transshipment_ids)) THEN 1
      ELSE 0 END) encounter_transshipment,
  (CASE
      WHEN event_type = 'rendezvous' AND (vessel_1_id IN (  SELECT  bunker_mmsi  FROM  bunker_ids) OR vessel_2_id IN (  SELECT  bunker_mmsi  FROM  bunker_ids)) THEN 1
      ELSE 0 END) encounter_bunker,
  (CASE
      WHEN event_type = 'rendezvous' AND (vessel_1_id IN (  SELECT  fishing_mmsi  FROM  fishing_ids) AND vessel_2_id IN (  SELECT  fishing_mmsi  FROM  fishing_ids)) THEN 1
      ELSE 0 END) encounter_fishing,
  (CASE
      WHEN event_type = 'coverage gap' THEN 1
      ELSE 0 END) coverage_gap
FROM
  joined_table)
SELECT
  mmsi,
  departure_timestamp,
  departure_port,
  arrival_timestamp,
  arrival_port,
  SUM(encounter_transshipment) encounters_transshipment,
  SUM(encounter_bunker) encounters_bunker,
  SUM(encounter_fishing) encounters_fishing,
  SUM(coverage_gap) coverage_gaps
FROM
  final_event_table
GROUP BY
  mmsi,
  departure_timestamp,
  departure_port,
  arrival_timestamp,
  arrival_port
"

bq_table(project = project,table = "poc_events",dataset = "human_rights") %>% 
  bq_table_delete()

bq_project_query(project,sql, destination_table = bq_table(project = project,table = "poc_events",dataset = "human_rights"),
                 use_legacy_sql = FALSE, allowLargeResults = TRUE)
```
# Extract AIS info from those voyages

```{r}
# Get NTZ area of each EEZ
# Data from https://www.protectedplanet.net/marine
# Only interested in no-take area. Not interested in Anarctica
ntzs <- read.csv("../data/WDPA_Mar2018_marine-csv/WDPA_Mar2018_marine-csv.csv",stringsAsFactors = FALSE) %>%
  filter(NO_TAKE == "All") %>%
  .$WDPAID %>%
  unique()

ntz_filter <- paste(paste0("regions LIKE '%mpant:",ntzs,"%'"),collapse=" OR ")

sql<-glue::glue("
#standardSQL
  WITH ping_info AS (
  SELECT
    mmsi,
    lat start_lat,
    lon start_lon,
    timestamp start_timestamp,
    next_lat end_lat,
    next_lon end_lon,
    next_timestamp end_timestamp,
    hours,
    avg_distance_km,
    eez_iso3,
    (CASE
        WHEN nnet_score = 1 AND NOT (distance_from_shore < 1000 AND implied_speed < 1) THEN hours
        ELSE 0 END) nnet_hours,
    (CASE
        WHEN {ntz_filter} THEN TRUE
        ELSE FALSE END) in_ntz
  FROM
    `world-fishing-827.gfw_research.nn`
  WHERE
    lat < 90
    AND lat > -90
    AND lon < 180
    AND lon >-180
    AND _PARTITIONTIME BETWEEN TIMESTAMP('2012-01-01')
    AND TIMESTAMP('2017-12-31')
    AND mmsi IN (
    SELECT
      mmsi
    FROM
      `human_rights.poc_voyages_with_anchorages`)),
  voyage_info AS(
  SELECT
    mmsi,
    flag,
    departure_port,
    departure_timestamp,
    arrival_timestamp,
    arrival_port,
    gear,
    engine_power
  FROM
    `ucsb-gfw.human_rights.poc_voyages_with_anchorages`),
  ais_info AS(
  SELECT
    ping_info.mmsi mmsi,
    voyage_info.flag flag,
    voyage_info.gear gear,
    voyage_info.engine_power engine_power,
    DATE_TRUNC(DATE(ping_info.start_timestamp), MONTH) month,
    DATE_TRUNC(DATE(ping_info.start_timestamp), DAY) day,
    ping_info.start_lat start_lat,
    ping_info.start_lon start_lon,
    ping_info.start_timestamp,
    ping_info.hours hours,
    ping_info.nnet_hours nnet_hours,
    ping_info.avg_distance_km avg_distance_km,
    voyage_info.departure_port departure_port,
    voyage_info.departure_timestamp departure_timestamp,
    voyage_info.arrival_port arrival_port,
    voyage_info.arrival_timestamp arrival_timestamp,
    (NOT ping_info.eez_iso3 IS NULL AND NOT ping_info.eez_iso3 = voyage_info.flag AND ping_info.nnet_hours > 0) fishing_foreign_eez,
    (ping_info.eez_iso3 IS NULL AND ping_info.nnet_hours > 0) fishing_high_seas,
    (ping_info.in_ntz AND ping_info.nnet_hours > 0) fishing_ntz
  FROM
    ping_info
  LEFT JOIN
    voyage_info
  ON
    ping_info.mmsi = voyage_info.mmsi
    AND ping_info.start_timestamp > voyage_info.departure_timestamp
    AND ping_info.start_timestamp < voyage_info.arrival_timestamp)
SELECT
  *
FROM
  ais_info
"
)

bq_table(project = project,table = "poc_voyage_ais_positions",dataset = "human_rights") %>% 
  bq_table_delete()
bq_project_query(project,query = sql, destination_table =  bq_table(project = project,table = "poc_voyage_ais_positions",dataset = "human_rights"),
                 use_legacy_sql = FALSE, allowLargeResults = TRUE)
```

# Grid AIS positions
```{r}
grid_size <- 0.5 # Grid in degrees
suspicious_cutff <- 4 # How many standard deviations from mean does revenue/cost ratio need to be to be suspicious?
sql <-glue::glue("
#standardSQL
  WITH grid_base AS(
  SELECT
    mmsi,
    gear,
    flag,
    month,
    engine_power,
    FLOOR(start_lat/{grid_size}) * {grid_size} lat_bin,
    FLOOR(start_lon/{grid_size}) * {grid_size} lon_bin,
    departure_port,
    departure_timestamp,
    DATE(departure_timestamp) departure_date,
    arrival_port,
    arrival_timestamp,
    SUM(hours) hours,
    SUM(nnet_hours) fishing_hours,
    SUM(hours - nnet_hours) * engine_power travel_effort_kWH,
    SUM(nnet_hours) * engine_power fishing_effort_kWH,
    SUM(avg_distance_km) distance_km,
    (SUM(CASE WHEN fishing_foreign_eez THEN 1 ELSE 0 END) > 0) fishing_foreign_eez,
    (SUM(CASE WHEN fishing_high_seas THEN 1 ELSE 0 END) > 0) fishing_high_seas,
    (SUM(CASE WHEN fishing_ntz THEN 1 ELSE 0 END) > 0) fishing_ntz
  FROM
    `human_rights.poc_voyage_ais_positions`
  WHERE
    NOT flag IS NULL
  GROUP BY
    mmsi,
    gear,
    flag,
    month,
    engine_power,
    lat_bin,
    lon_bin,
    departure_port,
    departure_timestamp,
    departure_date,
    arrival_port,
    arrival_timestamp),
  voyage_info AS(
  SELECT
    mmsi voy_mmsi,
    gear voy_gear,
    flag voy_flag,
    month voy_month,
    departure_port voy_departure_port,
    departure_timestamp voy_departure_timestamp,
    SUM(hours - nnet_hours) * engine_power voyage_travel_effort_kWH,
    SUM(nnet_hours) * engine_power voyage_fishing_effort_kWH
  FROM
    `human_rights.poc_voyage_ais_positions`
  GROUP BY
    mmsi,
    gear,
    flag,
    month,
    engine_power,
    departure_port,
    departure_timestamp),
  voyage_grids AS(
  SELECT
    *
  FROM
    grid_base
  LEFT JOIN
    voyage_info
  ON
    grid_base.mmsi = voyage_info.voy_mmsi
    AND grid_base.gear = voyage_info.voy_gear
    AND grid_base.flag = voyage_info.voy_flag
    AND grid_base.month = voyage_info.voy_month
    AND grid_base.departure_port = voyage_info.voy_departure_port
    AND grid_base.departure_timestamp = voyage_info.voy_departure_timestamp),
  voyage_grids_2 AS(
  SELECT
    *
    EXCEPT(voy_mmsi, voy_gear, voy_flag, voy_month, voy_departure_port,voy_departure_timestamp),
    (CASE WHEN fishing_effort_kWH >0 THEN fishing_effort_kWH / (voyage_travel_effort_kWH * fishing_effort_kWH / voyage_fishing_effort_kWH + fishing_effort_kWH)
      ELSE NULL
      END) revenue_cost_ratio
  FROM
    voyage_grids),
  summary_grids AS(
  SELECT
    flag sum_flag,
    gear sum_gear,
    month sum_month,
    lat_bin sum_lat_bin,
    lon_bin sum_lon_bin,
    AVG(revenue_cost_ratio) mean_revenue_cost_ratio,
    STDDEV(revenue_cost_ratio) sd_revenue_cost_ratio
  FROM
    voyage_grids_2
  GROUP BY
    sum_flag,
    sum_gear,
    sum_month,
    sum_lat_bin,
    sum_lon_bin)
SELECT
  *,
  (revenue_cost_ratio < mean_revenue_cost_ratio - {suspicious_cutff} * sd_revenue_cost_ratio) suspicious_econ
FROM
  voyage_grids_2
LEFT JOIN
  summary_grids
ON
  voyage_grids_2.flag = summary_grids.sum_flag
  AND voyage_grids_2.gear = summary_grids.sum_gear
  AND voyage_grids_2.month = summary_grids.sum_month
  AND voyage_grids_2.lat_bin = summary_grids.sum_lat_bin
  AND voyage_grids_2.lon_bin = summary_grids.sum_lon_bin
  ")
bq_table(project = project,table = "poc_voyages_gridded",dataset = "human_rights") %>% 
  bq_table_delete()
bq_project_query(project,query = sql, destination_table = bq_table(project = project,table = "poc_voyages_gridded",dataset = "human_rights"),
                 allowLargeResults = TRUE)
```

# Create voyage-level summaries
```{r}
sql<-glue::glue("
#standardSQL
  WITH main_voyage AS(
  SELECT
    mmsi,
    gear,
    flag,
    EXTRACT(YEAR
    FROM
      departure_timestamp) AS year,
    departure_port,
    departure_timestamp,
    departure_date,
    arrival_port,
    arrival_timestamp,
    SUM(hours) time_at_sea_hours,
    SUM(fishing_hours) fishing_hours,
    SUM(distance_km) distance_traveled_km,
    (SUM(CASE
          WHEN fishing_foreign_eez THEN 1
          ELSE 0 END) > 0) fishing_foreign_eez,
    (SUM(CASE
          WHEN fishing_high_seas THEN 1
          ELSE 0 END) > 0) fishing_high_seas,
    (SUM(CASE
          WHEN fishing_ntz THEN 1
          ELSE 0 END) > 0) fishing_ntz,
    (SUM(CASE
          WHEN suspicious_econ THEN 1
          ELSE 0 END)) / COUNT(*) fraction_suspicious_econ
  FROM
    `human_rights.poc_voyages_gridded`
  GROUP BY
    mmsi,
    gear,
    flag,
    departure_port,
    departure_timestamp,
    departure_date,
    arrival_port,
    arrival_timestamp),
  daily_fishing AS(
  SELECT
    mmsi,
    gear,
    flag,
    departure_port,
    departure_timestamp,
    (CASE
        WHEN SUM(hours) = 0 THEN NULL
        ELSE SUM(hours) END) daily_hours,
    day
  FROM
    `human_rights.poc_voyage_ais_positions`
  GROUP BY
    mmsi,
    gear,
    flag,
    departure_port,
    departure_timestamp,
    day),
  daily_fishing_sum AS(
  SELECT
    mmsi sum_mmsi,
    gear sum_gear,
    flag sum_flag,
    departure_port sum_departure_port,
    departure_timestamp sum_departure_timestamp,
    AVG(daily_hours) mean_daily_fishing_hours
  FROM
    daily_fishing
  GROUP BY
    mmsi,
    gear,
    flag,
    departure_port,
    departure_timestamp),
  main_voyage2 AS(
  SELECT
    * EXCEPT(sum_mmsi,
      sum_gear,
      sum_flag,
      sum_departure_port,
      sum_departure_timestamp)
  FROM
    main_voyage
  LEFT JOIN
    daily_fishing_sum
  ON
    main_voyage.mmsi = daily_fishing_sum.sum_mmsi
    AND main_voyage.gear = daily_fishing_sum.sum_gear
    AND main_voyage.flag = daily_fishing_sum.sum_flag
    AND main_voyage.departure_port = daily_fishing_sum.sum_departure_port
    AND main_voyage.departure_timestamp = daily_fishing_sum.sum_departure_timestamp),
  summary_voyages AS(
  SELECT
    flag sum2_flag,
    gear sum2_gear,
    year sum2_year,
    departure_port sum2_departure_port,
    arrival_port sum2_arrival_port,
    AVG(time_at_sea_hours) mean_time_at_sea_hours,
    STDDEV(time_at_sea_hours) sd_time_at_sea_hours,
    AVG(fishing_hours) mean_fishing_hours,
    STDDEV(fishing_hours) sd_fishing_hours,
    AVG(distance_traveled_km) mean_distance_traveled_km,
    STDDEV(distance_traveled_km) sd_distance_traveled_km,
    AVG(mean_daily_fishing_hours) mean_mean_daily_fishing_hours,
    STDDEV(mean_daily_fishing_hours) sd_mean_daily_fishing_hours
  FROM
    main_voyage2
  GROUP BY
    sum2_flag,
    sum2_gear,
    sum2_year,
    sum2_departure_port,
    sum2_arrival_port),
  event_table AS(
  SELECT
    mmsi events_mmsi,
    departure_timestamp events_departure_timestamp,
    departure_port events_departure_port,
    arrival_timestamp events_arrival_timestamp,
    arrival_port events_arrival_port,
    encounters_transshipment,
    encounters_bunker,
    encounters_fishing,
    coverage_gaps
  FROM
    `human_rights.poc_events` ),
  penultimate AS (
  SELECT
    * EXCEPT(sum2_gear,
      sum2_flag,
      sum2_year,
      sum2_departure_port,
      sum2_arrival_port,
      mean_time_at_sea_hours,
      sd_time_at_sea_hours,
      mean_fishing_hours,
      sd_fishing_hours,
      mean_distance_traveled_km,
      sd_distance_traveled_km,
      mean_mean_daily_fishing_hours,
      sd_mean_daily_fishing_hours,
      events_mmsi,
      events_departure_timestamp,
      events_departure_port,
      events_arrival_timestamp,
      events_arrival_port),
    (time_at_sea_hours > mean_time_at_sea_hours + {suspicious_cutff} * sd_time_at_sea_hours) suspicious_time_at_sea_hours,
    (fishing_hours > mean_fishing_hours + {suspicious_cutff} * sd_fishing_hours) suspicious_fishing_hours,
    (distance_traveled_km > mean_distance_traveled_km + {suspicious_cutff} * sd_distance_traveled_km) suspicious_distance_traveled_km,
    (mean_daily_fishing_hours > mean_mean_daily_fishing_hours + {suspicious_cutff} * sd_mean_daily_fishing_hours) suspicious_mean_daily_fishing_hours,
    encounters_transshipment >0 suspicious_encounters_transshipment,
    encounters_bunker >0 suspicious_encounters_bunker,
    encounters_fishing >0 suspicious_encounters_fishing,
    coverage_gaps >0 suspicious_coverage_gaps
  FROM
    main_voyage2
  LEFT JOIN
    summary_voyages
  ON
    main_voyage2.gear = summary_voyages.sum2_gear
    AND main_voyage2.flag = summary_voyages.sum2_flag
    AND main_voyage2.year = summary_voyages.sum2_year
    AND main_voyage2.departure_port = summary_voyages.sum2_departure_port
    AND main_voyage2.arrival_port = summary_voyages.sum2_arrival_port
  LEFT JOIN
    event_table
  ON
    main_voyage2.mmsi = event_table.events_mmsi
    AND main_voyage2.departure_timestamp = event_table.events_departure_timestamp
    AND main_voyage2.departure_port = event_table.events_departure_port
    AND main_voyage2.arrival_timestamp = event_table.events_arrival_timestamp
    AND main_voyage2.arrival_port = event_table.events_arrival_port),
  penultimate2 AS(
  SELECT
    mmsi,
    gear,
    flag,
    year,
    departure_port,
    departure_date,
    departure_timestamp,
    arrival_port,
    arrival_timestamp,
    time_at_sea_hours,
    fishing_hours,
    distance_traveled_km,
    mean_daily_fishing_hours,
    fraction_suspicious_econ,
    encounters_transshipment,
    encounters_bunker,
    encounters_fishing,
    coverage_gaps,
    (CASE
        WHEN fishing_foreign_eez THEN 1
        ELSE 0 END) fishing_foreign_eez,
    (CASE
        WHEN fishing_high_seas THEN 1
        ELSE 0 END) fishing_high_seas,
    (CASE
        WHEN fishing_ntz THEN 1
        ELSE 0 END) fishing_ntz,
    (CASE
        WHEN fraction_suspicious_econ > 0 THEN 1
        ELSE 0 END) suspicious_econ,
    (CASE
        WHEN suspicious_fishing_hours THEN 1
        ELSE 0 END) suspicious_fishing_hours,
    (CASE
        WHEN suspicious_time_at_sea_hours THEN 1
        ELSE 0 END) suspicious_time_at_sea_hours,
    (CASE
        WHEN suspicious_distance_traveled_km THEN 1
        ELSE 0 END) suspicious_distance_traveled_km,
    (CASE
        WHEN suspicious_mean_daily_fishing_hours THEN 1
        ELSE 0 END) suspicious_mean_daily_fishing_hours,
    (CASE
        WHEN suspicious_encounters_transshipment THEN 1
        ELSE 0 END) suspicious_encounters_transshipment,
    (CASE
        WHEN suspicious_encounters_bunker THEN 1
        ELSE 0 END) suspicious_encounters_bunker,
    (CASE
        WHEN suspicious_encounters_fishing THEN 1
        ELSE 0 END) suspicious_encounters_fishing,
    (CASE
        WHEN suspicious_coverage_gaps THEN 1
        ELSE 0 END) suspicious_coverage_gaps
  FROM
    penultimate)
SELECT
  *,
  (fishing_foreign_eez + fishing_high_seas + fishing_ntz + suspicious_econ + suspicious_fishing_hours + suspicious_time_at_sea_hours + suspicious_distance_traveled_km + suspicious_mean_daily_fishing_hours + suspicious_encounters_transshipment + suspicious_encounters_bunker + suspicious_encounters_fishing + suspicious_coverage_gaps) risk_score
FROM
  penultimate2
ORDER BY risk_score DESC")

bq_table(project = project,table = "poc_voyages",dataset = "human_rights") %>% 
  bq_table_delete()
bq_project_query(project,query = sql, destination_table = bq_table(project = project,table = "poc_voyages",dataset = "human_rights"),
                 allowLargeResults = TRUE)

```

```{r}
sql<-"
SELECT
*
FROM
`human_rights.poc_voyages`
"
results <- bq_project_query(project, sql) %>%
  bq_table_download(max_results = Inf)

temp_file_name = tempfile(fileext=".csv")
drive_download(file="Forced Labor Vessel Database",path=temp_file_name,overwrite=TRUE)
vessel_database <- read_csv(temp_file_name)

thai_mmsi <- vessel_database %>%
  filter(`Flag vessel flies` == "Thailand") %>%
  .$MMSI

risky_vessels <- results %>% 
  group_by(mmsi,year) %>% 
  summarize(max_risk_score = max(risk_score)) %>%
  mutate(on_list = ifelse(mmsi %in% thai_mmsi,TRUE,FALSE)) %>%
  arrange(desc(max_risk_score))
```

